---
title: "Project2"
author: "Michael Im"
date: "April 9, 2017"
output:   
  html_document: 
    theme: united
    toc: yes
    number_sections: TRUE
    toc_float:
      collapsed: TRUE
---

#Introduction

```{r, include = F}

data1 = read.csv("sdclean.csv", header = T)

```

##Cleaning Data

```{r}
#who will match on this dataset

#getting the numerical variables
str(data1)
num = sapply(data1, is.numeric)
nums = data1[,num]

train1 = data1[1:5000,]
test1 = data1[5001:6000,]

train2 = data1[1:5000,]
test2 = data1[5001:6000,]
#tele_nn <- model.matrix(~ job + marital + education + default + housing + loan +  contact + month + day_of_week + poutcome + y, data1 = tele1)
```

#Building the Logistic Model

##Basic Model - All Variables

```{r}
#log model 1 with ALL VARIABLES

#building logistic model with the numerical variables
log1 = glm(match ~ ., data = train1, family = "binomial")
summary(log1)
#significant variable: gender + int_corr + age_o + samerace + race_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o + race + imprace + sports + exercise + art + gaming + clubbing + reading + tv + movies + concerts + music + shopping + yoga + exphappy + attr2_1 + sinc2_1 + intel2_1 + fun2_1 + amb2_1 + shar2_1
#note all significant at 90% confidence interval

```

##90% Confidence Interval Regression (Workdown)

###Model 1

```{r}

#log model 2 with VARIABLES THAT WERE 90% CONFIDENT FROM FIRST MODEL

#building logistic model with the numerical variables
log2 = glm(match ~ gender + int_corr + age_o + samerace + race_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o + race + imprace + sports + exercise + art + gaming + clubbing + reading + tv + movies + concerts + music + shopping + yoga + exphappy + attr2_1 + sinc2_1 + intel2_1 + fun2_1 + amb2_1 + shar2_1, data = train1, family = "binomial")
summary(log2)
#variables to include for next model: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + clubbing +  tv + movies + concerts + music + shopping +  exphappy + attr2_1 + sinc2_1 + intel2_1 + fun2_1 + amb2_1 

#VARIABLES THAT WE TOOK OUT (stage 1)
#gender + samerace + race_o + race + sports + reading + yoga + shar2_1

```

###Model 2

```{r}
#log model 3 with VARIABLES THAT WERE 90% CONFIDENT FROM THE SECOND MODEL

#building logistic model with the numerical variables
log3 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + clubbing +  tv + movies + concerts + music + shopping +  exphappy + attr2_1 + sinc2_1 + intel2_1 + fun2_1 + amb2_1, data = train1, family = "binomial")
summary(log3)
#variables to include for next model: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + clubbing +  tv + movies + concerts + music + exphappy + attr2_1 + intel2_1

#VARIABLES THAT WE TOOK OUT (stage 2)
#shopping + sinc2_1 + fun2_1 + amb2_1
```

###Model 3

```{r}

#log model 4 with VARIABLES THAT WERE 90% CONFIDENT FROM THE THIRD MODEL

#building logistic model with the numerical variables
log4 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + clubbing +  tv + movies + concerts + music + exphappy + attr2_1 + intel2_1, data = train1, family = "binomial")
summary(log4)
#variables to include for next model: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + clubbing + movies + concerts + music + exphappy + attr2_1 + intel2_1

#VARIABLES THAT WE TOOK OUT (stage 2)
#tv

```

###Model 4

```{r}

#log model 5 with VARIABLES THAT WERE 90% CONFIDENT FROM THE FOURTH MODEL

#building logistic model with the numerical variables
log5 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + clubbing + movies + concerts + music + exphappy + attr2_1 + intel2_1, data = train1, family = "binomial")
summary(log5)
#variables to include for next model: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + movies + concerts + music + exphappy + attr2_1 + intel2_1

#VARIABLES THAT WE TOOK OUT (stage 2)
#clubbing

```

###Model 5

```{r}

#log model 6 with VARIABLES THAT WERE 90% CONFIDENT FROM THE FIFTH MODEL

#building logistic model with the numerical variables
log6 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + movies + concerts + music + exphappy + attr2_1 + intel2_1, data = train1, family = "binomial")
summary(log6)
#variables to include for next model: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + prob_o + met_o +  imprace +  exercise + art + gaming + movies + concerts + music + exphappy + attr2_1 + intel2_1

#ALL VARIABLES ARE NOW CONFIDENT AT THE 90% LEVEL
#BONUS: ACTUALLY ALL THE VARIABLES ARE NOW 95% CONFIDENT AS WELL

```

##Logistic Model Including non-numerical Values

###Model 1

```{r}

#building logistic model with the numerical variables
log_all1 = glm(match ~ ., data = train2, family = "binomial")
summary(log_all1)
#significant variable: gender + int_corr + age_o + samerace + race_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + race + goal + career_c + imprace + sports + exercise + art + gaming + clubbing + tv + theater + movies + concerts + yoga + exphappy + attr2_1 + sinc2_1 + intel2_1 + fun2_1 + amb2_1 + shar2_1
#note all significant at 90% confidence interval

```

###Model 2

```{r}

#building logistic model with the numerical variables
log_all3 = glm(match ~ gender + int_corr + age_o + samerace + race_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + race + goal + career_c + imprace + sports + exercise + art + gaming + clubbing + tv + theater + movies + concerts + yoga + exphappy + attr2_1 + sinc2_1 + intel2_1 + fun2_1 + amb2_1 + shar2_1, data = train2, family = "binomial")
summary(log_all3)
#significant variable: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + goal + career_c + imprace + exercise + gaming + clubbing + movies + concerts + exphappy + attr2_1 + sinc2_1 + intel2_1
#note all significant at 90% confidence interval

#VARIABLES THAT WE TOOK OUT
#gender + samerace + race_o + race + sports + + art + tv + theater + yoga + fun2_1 + amb2_1 + shar2_1


```

###Model 3

```{r}

#building logistic model with the numerical variables
log_all4 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + goal + career_c + imprace + exercise + gaming + clubbing + movies + concerts + exphappy + attr2_1 + sinc2_1 + intel2_1, data = train2, family = "binomial")
summary(log_all4)
#significant variable: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + goal + career_c + imprace + exercise + gaming + clubbing + movies + concerts + exphappy + attr2_1 + intel2_1
#note all significant at 90% confidence interval

#VARIABLES THAT WE TOOK OUT
#sinc2_1


```

###Model 4

```{r}

#building logistic model with the numerical variables
log_all5 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + goal + career_c + imprace + exercise + gaming + clubbing + movies + concerts + exphappy + attr2_1 + intel2_1, data = train2, family = "binomial")
summary(log_all5)
#significant variable: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + goal + career_c + imprace + exercise + gaming + movies + concerts + exphappy + attr2_1 + intel2_1
#note all significant at 90% confidence interval

#VARIABLES THAT WE TOOK OUT
#clubbing


```

###Model 5

```{r}

#building logistic model with the numerical variables
log_all6 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + goal + career_c + imprace + exercise + gaming + movies + concerts + exphappy + attr2_1 + intel2_1, data = train2, family = "binomial")
summary(log_all6)
#significant variable: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + career_c + imprace + exercise + gaming + movies + concerts + exphappy + attr2_1 + intel2_1
#note all significant at 90% confidence interval

#VARIABLES THAT WE TOOK OUT
#goal


```

###Model 6

```{r}

#building logistic model with the numerical variables
log_all7 = glm(match ~ int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + career_c + imprace + exercise + gaming + movies + concerts + exphappy + attr2_1 + intel2_1, data = train2, family = "binomial")
summary(log_all7)
#significant variable: int_corr + age_o + pf_o_sin + pf_o_sha + attr_o + fun_o + amb_o + prob_o + met_o + career_c + imprace + exercise + gaming + movies + concerts + exphappy + attr2_1 + intel2_1
#note all significant at 90% confidence interval

#NOTE THAT THE ONLY CAREER THAT IS 90% SIGNIFICANT IS A CAREER IN POLITICS AND UNDECIDED AND BOTH RESULT IN SERIOUS LOSS OF CHANCE IN GETTING MATCHED (lol)


```

##Final Logistic Models

```{r}

summary(log6)
summary(log_all7)

```

###Predictions from Logistic Models (only numeric variables)

```{r}

#log6 = predict.model.log6
#log_all7 = predict.model.log_all7

prop.table(table(test1$match))

# Predict the Match Probability for the Testing Dataset using the model developed on the training dataset
#use survival.model2
predict.model.log6 = predict(log6, newdata = test1, type = "response")
predict.model.log6 = as.data.frame(predict.model.log6, na.rm = TRUE)
predict.model.log6$predict.model <- as.numeric(predict.model.log6$predict.model)
predict.model.log6$match <- ifelse(predict.model.log6$predict.model > 0.5, 1, 0)
predict.model.log6$X <- test1$X
predict.model.log6
prop.table(table(predict.model.log6$match))

```

###Predictions from Logistic Models (all variables)

```{r}

#log6 = predict.model.log6
#log_all7 = predict.model.log_all7
prop.table(table(test2$match))

# Predict the Match Probability for the Testing Dataset using the model developed on the training dataset
#use survival.model2
predict.model.log_all7 = predict(log_all7, newdata = test2, type = "response")
predict.model.log_all7 = as.data.frame(predict.model.log_all7, na.rm = TRUE)
predict.model.log_all7$predict.model <- as.numeric(predict.model.log_all7$predict.model)
predict.model.log_all7$match <- ifelse(predict.model.log_all7$predict.model > 0.5, 1, 0)
predict.model.log_all7$X <- test2$X
predict.model.log_all7
prop.table(table(predict.model.log_all7$match))

```


#Possible Ideas

* Logistic Regression with interactions
  + Mixing up some of the characteristics
  + Combining the interests and patterns (high interest in sports and sports)
  + Mixing characteristics that seem to clash (like shopping and sports)
* Have an RShiny that has data of person you want to match with, and allows you to change your characteristics of yourself to see if you match with that person











